---
title: "Peak Bloom Prediction Demo"
author: "Quang Nguyen"
date: "02/28/2022"
output:
  html_document:
    df_print: kable
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, error = FALSE, 
                      message = FALSE,
                      fig.align = 'center',
                      out.width = '80%')
```

## Data Exploration 

Loading packages  

```{r}
library(tsibble)
library(fable)
library(tidyverse)
library(ggsci)
```
Loading data  

```{r load_data}
main_dfs <- c("kyoto.csv", "liestal.csv", "washingtondc.csv")
df <- map(main_dfs, ~read.csv(file = file.path("data", .x)))
df <- do.call(bind_rows, df)
df <- df %>% filter(year >= 1888) %>% 
  select(location, year, bloom_doy) %>% as_tsibble(index = year, key = location)
print(df)
```
```{r plot_trend}
autoplot(df) + theme_minimal() + scale_color_npg() + 
  labs(x = "Year", y = "Day of Year with Bloom")
```
The data it seems has both periodicity and trend. In other words, there are cycles of when the date of bloom is earlier in the year while others is late, however there is a consistent trend of the bloom date being later in the year. 

Let's attach some timeseries together and explore some relationships between external data and our current forecasting window:  
```{r}

korea <- read.csv(file = file.path("data", "south_korea.csv"))

korea


```








## Model formulation 

## Evaluation 

## Prediction  

